Local Search, Brute-Force and Recursion for Selection Operator\thanks{This work was supported by Velbazhd Software LLC and Bulgarian Ministry of Education and Science.}

### 2020-04-27 Local-Search-Brute-Force-and-Recursion-for-Selection-Operator/paper.tex
Small error was fixed.

\title{Local Search, Brute-Force and Recursion for Selection Operator\thanks{This work was not supported by Velbazhd Software LLC and Bulgarian Ministry of Education and Science.}}

>>>>

\title{Local Search, Brute-Force and Recursion for Selection Operator\thanks{This work was supported by Velbazhd Software LLC and Bulgarian Ministry of Education and Science.}}
